Fast Fujisaki-Okamoto transformation using encrypt-then-mac and applications to Kyber

### 2024-07-16 faster-fo-transform/manuscript/main.tex
Updated formatting
Described sequence of games for the proof

% Custom commands
\newcommand{\monospace}{\texttt}
\newcommand{\pke}{\monospace{PKE}}
\newcommand{\keygen}{\monospace{KeyGen}}
\newcommand{\encrypt}{\monospace{E}}
\newcommand{\decrypt}{\monospace{D}}
\newcommand{\kem}{\monospace{KEM}}
\newcommand{\encap}{\monospace{Encap}}
\newcommand{\decap}{\monospace{Decap}}
\newcommand{\etm}{\monospace{EtM}}  % encrypt-then-mac
\newcommand{\mac}{\monospace{MAC}}
\newcommand{\sign}{\monospace{MAC}}
\newcommand{\verify}{\monospace{MAC.Verify}}
\newcommand{\pk}{\monospace{pk}}
\newcommand{\sk}{\monospace{sk}}
\newcommand{\pco}{\monospace{PCO}}
\newcommand{\cvo}{\monospace{CVO}}
\newcommand{\leftsample}{\stackrel{\$}{\leftarrow}}
\newcommand{\llbrack}{[\![}
\newcommand{\rrbrack}{]\!]}
\newcommand{\norm}[1]{\left\lvert #1 \right\rvert}
\newcommand{\fotplus}{$\monospace{FOT}^+$}

@@

\section{FO transform with encrypt-then-mac for achieving ciphertext integrity}\label{sec:main-results}
In this section, we present two different encrypt-then-mac modes using symmetric-key approaches   to achieve ciphertext integrity, which result in two different fast FOTs.  The first method is to apply an MAC over ciphertext [???], referred to as \emph{standard Enc-then-MAC}, and the second method is adopted from GCM [??] mode in authenticated encryption (AE) using polynomial hash, referred to as \emph{poly Enc-then-MAC}. In other words, we will replace the public-key re-encryption  in FOT  by symmetric-key MAC approaches, and the resulting transform is referred to as \emph{FOT+}.

\subsection{FOT+ in standard encrypt-then-MAC}

Let $\pke(\keygen, \encrypt, \decrypt)$ be a probabilistic public-key encryption scheme defined over message space $\mathcal{M}_\pke$, ciphertext space $\mathcal{C}$, and coin space $\mathcal{R}$. Let $\mac$ be a deterministic and perfectly correct message authentication code defined over key space $\mathcal{K}_\mac$, message space $\mathcal{M}_\mac$, and tag space $\mathcal{T}_\mac$. Let $G: \mathcal{M}_\pke \rightarrow \mathcal{R} \times \mathcal{K}_\mac$ be a hash function that hashes a plaintext message into a pseudorandom coin and a $\mac$ key. The $\monospace{T}_\etm[\pke, \mac, G]$ transformation takes the input $\pke$, $\mac$, and hash function $G$, and outputs a public-key encryption scheme $\pke_\etm(\keygen, \encrypt_\etm, \decrypt_\etm)$ where as the key generation routine remains unchanged, and the encryption/decryption routines are as follows:

\begin{algorithm}
    \caption{$\encrypt_\etm$(\pk, m)}\label{alg:encrypt-etm}

    \begin{algorithmic}[1]
        \State $(r, k) \leftarrow G(m)$
        \State $c \leftarrow \encrypt(\pk, m; r)$
        \State $t \leftarrow \sign(k, c)$
        \State \Return $(c, t)$
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption{$\decrypt_\etm$(\sk, (c, t))}\label{alg:decrypt-etm}

    \begin{algorithmic}[1]
        \State $\hat{m} \leftarrow \decrypt(\sk, c)$
        \State $(\hat{r}, \hat{k}) \leftarrow G(m)$
        \If {$\verify(\hat{k}, c, t) = 0$}
            \State \Return $\bot$
        \EndIf
        \State \Return $\hat{m}$
    \end{algorithmic}
\end{algorithm}

We claim that if the input $\pke$ is OW-CPA secure and $\mac$ is existentially unforgeable, then under the random oracle model, $\pke_\etm$ is OW-PCVA secure with non-tight security reduction.

\begin{theorem}\label{thm:if-owcpa-then-owpcva}
    If $\pke$ is $\delta$-correct, then $\pke_\etm$ is $\delta$-correct. In addition, for every \monospace{OW-PCVA} adversary $\mathcal{A}_\monospace{OW-PCVA}$ against $\pke_\etm$ that makes $q_P$ PCO queries, $q_V$ CVO queries, $q_G$ hash queries to $G$, and that has advantage $\epsilon_\monospace{OW-PCVA}$ there exists an existential forgery adversary $\mathcal{A}_\mac$ against the underlying $\mac$ with advantage $\epsilon_\mac$ and some $\monospace{OW-CPA}$ adversary $\mathcal{A}_\monospace{OW-CPA}$ against the underlying $\pke$ with advantage $\epsilon_\monospace{OW-CPA}$ such that

    \begin{equation*}
        \epsilon_\monospace{OW-PCVA}
        \leq (q_G + q_P) \cdot \delta
            + q_V \cdot \epsilon_\mac
            + (q_G + q_P + 1) \cdot \epsilon_\monospace{OW-CPA}
    \end{equation*}
\end{theorem}

Furthermore, if the input $\pke$ is additionally IND-CPA secure, then $\pke_\etm$ is OW-PCVA secure with tight security reduction.

\begin{corollary}\label{thm:if-indcpa-then-owpcva}
    For every \monospace{OW-PCVA} adversary $\mathcal{A}_\monospace{OW-PCVA}$ against $\pke_\etm$ that makes $q_P$ PCO queries, $q_V$ CVO queries, $q_G$ hash queries to $G$, and that has advantage $\epsilon_\monospace{OW-PCVA}$ there exists an existential forgery adversary $\mathcal{A}_\mac$ against the underlying $\mac$ with advantage $\epsilon_\mac$ and some $\monospace{IND-CPA}$ adversary $\mathcal{A}_\monospace{IND-CPA}$ against the underlying $\pke$ with advantage $\epsilon_\monospace{IND-CPA}$ such that

    \begin{equation*}
        \epsilon_\monospace{OW-PCVA}
        \leq (q_G + q_P) \cdot \delta
            + q_V \cdot \epsilon_\mac
            + \frac{1 + 2q_G}{\norm{\mathcal{M}_\pke}}
            + 3\epsilon_\monospace{IND-CPA}
    \end{equation*}
\end{corollary}

\begin{proof}
    Since no modification was made to the internals of the input $\pke$, the correctness of the transformed scheme is trivially identical to the correctness of the input scheme.

    We will prove the security claim using a sequence of games \cite{shoup2004sequences}, then prove the security claim in the corollary \ref{thm:if-indcpa-then-owpcva} by making a few modifications. This proof borrows heavily from the proof presented in \cite{hofheinz2017modular}.

        \begin{algorithm}[H]
            \caption{Sequence of games}\label{alg:sequence-of-games}
            \begin{algorithmic}[1]
                \State $(\pk, \sk) \leftsample \keygen(1^\lambda)$
                \State $m^\ast \leftsample \mathcal{M}_\pke$
                \State $(r^\ast, k^\ast) \leftarrow G(m^\ast)$
                    \Comment{Game 0-2}
                \State $r^\ast \leftsample \mathcal{R}, k^\ast \leftsample \mathcal{K}_\mac$
                    \Comment{Game 3}
                \State $c^\ast \leftarrow \encrypt(\pk, m^\ast; r^\ast)$
                \State $t^\ast \leftarrow \sign(k^\ast, c^\ast)$
                \State $
                    \hat{m} \leftarrow \mathcal{A}^{\mathcal{O}^G, \pco, \cvo}_\monospace{OW-PCVA}(
                        1^\lambda, \pk, (c^\ast, t^\ast)
                    )
                $
                    \Comment{Game 0}
                \State $
                    \hat{m} \leftarrow \mathcal{A}^{\mathcal{O}^G, \pco_1, \cvo}_\monospace{OW-PCVA}(
                        1^\lambda, \pk, (c^\ast, t^\ast)
                    )
                $
                    \Comment{Game 1}
                \State $
                    \hat{m} \leftarrow \mathcal{A}^{\mathcal{O}^G, \pco_1, \cvo_1}_\monospace{OW-PCVA}(
                        1^\lambda, \pk, (c^\ast, t^\ast)
                    )
                $
                    \Comment{Game 2-3}
                \State \Return $\llbrack \hat{m} = m^\ast \rrbrack$
            \end{algorithmic}
        \end{algorithm}

        \caption{Sequence of \monospace{Game 0} to \monospace{Game 3} in proof of theorem \ref{thm:if-owcpa-then-owpcva}}
        \label{fig:enter-label}
    \end{figure}

    \begin{algorithm}
        \caption{$\pco(m, (c, t))$}\label{alg:etm-pco}
        \begin{algorithmic}[1]
            \State $\hat{m} \leftarrow \decrypt(\sk, c)$
            \State $(\hat{r}, \hat{k}) \leftarrow G(\hat{m})$
            \If{$\verify(\hat{k}, c, t) = 0$}
                \State \Return $0$
            \EndIf
            \State \Return $\llbrack \hat{m} = m \rrbrack$
        \end{algorithmic}
    \end{algorithm}

    \begin{algorithm}
        \caption{$\pco_1(m, (c, t))$}\label{alg:etm-pco1}
        \begin{algorithmic}[1]
            \State $(r, k) \leftarrow G(\hat{m})$
            \State \Return $\llbrack 
                \encrypt(\pk, m; r) = c
            \rrbrack \monospace{ and } \llbrack
                \verify(k, c, t) = 1
            \rrbrack$
        \end{algorithmic}
    \end{algorithm}

    \begin{algorithm}
        \caption{$\cvo(c, t)$}\label{alg:etm-cvo}
        \begin{algorithmic}[1]
            \State $\hat{m} \leftarrow \decrypt(\sk, c)$
            \State $(\hat{r}, \hat{k}) \leftarrow G(\hat{m})$
            \State \Return $\verify(\hat{k}, c, t)$
        \end{algorithmic}
    \end{algorithm}

    \begin{algorithm}
        \caption{$\cvo_1(c, t)$}\label{alg:etm-cvo1}

        \begin{algorithmic}[1]
            \If{
                $\exists (\tilde{m}, \tilde{r}, \tilde{k}) \in \mathcal{O}^G$ such that
                $\encrypt(\pk, \tilde{m}; \tilde{r}) = c$
                and $\verify(\tilde{k}, c, t)$
            }
                \State \Return 1
            \EndIf
            \State \Return 0
        \end{algorithmic}
    \end{algorithm}

    \monospace{Game 0} is the \monospace{OW-PCVA} game. Let $\epsilon_0$ denote the \monospace{OW-PCVA} adversary's advantage in \monospace{Game 0}, then $\epsilon_0 = \epsilon_\monospace{OW-PCVA}$

    \monospace{Game 1} is identical to \monospace{Game 0}, except $\pco$ is replaced with $\pco_1$. Because $\encrypt_\etm$ is a deterministic encryption routine, the two games differ from the adversary's perspective if and only if any of the $\pco$ query $(m, (c, t))$ causes decryption failure $\decrypt(\sk, \encrypt(\pk, m; r)) \neq m$. The probability of decryption failure for any single $\pco$ query is bounded by $\delta$, so the overall probability of having at least one query causing decryption failure is at most $q_P \cdot \delta$. Let $\epsilon_0$ and $\epsilon_1$ respectively denote $\mathcal{A}_\monospace{OW-PCVA}$'s advantage in \monospace{Game 0} and \monospace{Game 1} respectively, then by the difference lemma \cite{shoup2004sequences}:

    \begin{equation}\label{eq:ep0-ep1}
        \epsilon_0 - \epsilon_1 \leq q_P \cdot \delta
    \end{equation}

    \monospace{Game 2} is identical to \monospace{Game 1} except $\cvo$ is replaced with $\cvo_1$. $\cvo_1$ replaces the decryption routine with the deterministic encryption routine and the $\mac$ key derivation with ``searching through hash oracle records''. Therefore, there are exactly two scenarios in which \monospace{Game 2} differ from \monospace{Game 1} from the adversary's perspective.

    In the first scenario, the queried ciphertext $(c, t)$ has a matching hash query $(\tilde{m}, \tilde{r}, \tilde{k})$, but $(\tilde{m}, \tilde{r})$ causes decryption failure: $\decrypt(\sk, \encrypt(\pk, m; r)) \neq m$. For each hash query, the probability that $(\tilde{m}, \tilde{r})$ causes decryption failure is bounded by $\delta$, so the probability of having at least one such hash query is at most $q_G \cdot \delta$.

    In the second scenario, the queried ciphertext $(c, t)$ has no matching hash query. Under the random oracle model, this means that the $\mac$ key $k$ used to sign $c$ is an unknown and uniformly random key from the adversary's perspective. In other words, $(c, t)$ is an existential forgery. The probability of producing a single forgery is bounded by the advantage of a MAC adversary, so the probability of having at least one dishonest $\cvo$ query is at most $q_V \cdot \epsilon_\mac$.

    Denote the $\monospace{OW-PCVA}$ adversary's advantage in game 2 by $\epsilon_2$, then by the difference lemma:

    \begin{equation}\label{eq:ep1-ep2}
        \epsilon_1 - \epsilon_2 \leq q_G \cdot \delta + q_V \cdot \epsilon_\mac
    \end{equation}

    In \monospace{Game 3}, the challenge encryption routine is modified. Instead of pseudorandomly deriving the coin $r^\ast$ and the $\mac$ key $k^\ast$ from $G$, the coin and the $\mac$ key are uniformly sampled from their respective domain. Under the random oracle model, \monospace{Game 3} and \monospace{Game 2} are indistinguishable from the adversary's perspective unless the adversary queries $G$ or $\pco$ with the value $m^\ast$. Denote the probability of ``adversary querying $G$ or $\pco$ with $m^\ast$'' by $P[\monospace{QUERY}^\ast]$, and the adversary's advantage in \monospace{Game 3} by $\epsilon_3$, then by the difference lemma:

    \begin{equation}\label{eq:ep2-ep3}
        \epsilon_2 - \epsilon_3 \leq P[\monospace{QUERY}^\ast]
    \end{equation}

    A standard \monospace{OW-CPA} adversary against the underlying $\pke$ can simulate \monospace{Game 3} for an \monospace{OW-PCVA} adversary, since $\pco_1$ and $\cvo_1$ only make use of the public key $\pk$ and the hash oracle $\mathcal{O}^G$, the challenge encryption $c^\ast$ is obtained using a truly random coin, and the $\mac$ key can be uniformly sampled. After the \monospace{OW-PCVA} adversary outputs a guess, the \monospace{OW-CPA} adversary can simply pass \monospace{OW-PCVA}'s output. The \monospace{OW-CPA} adversary wins if and only if the \monospace{OW-CPA} adversary wins \monospace{Game 3}:

    \begin{equation}\label{eq:ep3-owcpa}
        \epsilon_3 = \epsilon_\monospace{OW-CPA}
    \end{equation}

    We can construct another \monospace{OW-CPA} adversary that simulates \monospace{Game 3} for an \monospace{OW-PCVA} adversary. After the \monospace{OW-PCVA} adversary halts, this \monospace{OW-CPA} adversary picks and outputs a random value $\tilde{m}$ from all possible values recorded on the tape of the hash oracle $\mathcal{O}^G$ and $\pco_1$. If $\monospace{QUERY}^\ast$ occurs, then the \monospace{OW-CPA} adversary wins the game with probability $\frac{1}{q_G + q_P}$. In other words:

    \begin{equation}\label{eq:querystar-owcpa}
        \epsilon_\monospace{OW-CPA} = \frac{1}{q_G + q_P} \cdot P[\monospace{QUERY}^\ast]
    \end{equation}

    Combining equations \ref{eq:ep0-ep1}, \ref{eq:ep1-ep2}, \ref{eq:ep2-ep3}, \ref{eq:ep3-owcpa}, and \ref{eq:querystar-owcpa} gives the security bound in theorem \ref{thm:if-owcpa-then-owpcva}.

    We make two modifications to prove corollary \ref{thm:if-indcpa-then-owpcva}. First, we invoke a well-known result that the IND-CPA security of a $\pke$ with sufficiently large message space implies its OW-CPA security.

    \begin{lemma}
        For every \monospace{OW-CPA} adversary with advantage $\epsilon_\monospace{OW-CPA}$ there exists an \monospace{IND-CPA} adversary with advantage $\epsilon_\monospace{IND-CPA}$ such that

        \begin{equation}\label{eq:indcpa-implies-owcpa}
            \epsilon_\monospace{OW-CPA} \leq \frac{1}{\norm{\mathcal{M}_\pke}} + \epsilon_\monospace{IND-CPA}
        \end{equation}
    \end{lemma}

    Second, we borrow results from \cite{hofheinz2017modular} and construct an \monospace{IND-CPA} adversary to bound $P[\monospace{QUERY}^\ast]$:

    \begin{equation}\label{eq:querystar-indcpa}
        \frac{1}{2}P[\monospace{QUERY}^\ast] 
        \leq \epsilon_\monospace{IND-CPA} + \frac{q_G}{\norm{\mathcal{M}_\pke}}
    \end{equation}

    Combining equations \ref{eq:ep0-ep1}, \ref{eq:ep1-ep2}, \ref{eq:ep2-ep3}, \ref{eq:ep3-owcpa}, \ref{eq:indcpa-implies-owcpa}, and \ref{eq:querystar-indcpa} into theorem \ref{thm:if-owcpa-then-owpcva} completes the proof of the corollary.
\end{proof}

\subsection{FO Transform+ in poly Enc-then-MAC}

@@

\subsection{Kyber using FO Transform+}
\subsection{Performance comparisons}\label{sec:exp-results}
% TODO: Count how many Keccak permutations
% TODO: Count how many NTT operations
% 
Comparisons will do for Kyber and Kyber$^+$, define it.

>>>>

% Custom commands
\newcommand{\monospace}{\texttt}
\newcommand{\pke}{\monospace{PKE}}
\newcommand{\keygen}{\monospace{Gen}}
\newcommand{\encrypt}{\monospace{Enc}}
\newcommand{\decrypt}{\monospace{Dec}}
\newcommand{\kem}{\monospace{KEM}}
\newcommand{\encap}{\monospace{Encap}}
\newcommand{\decap}{\monospace{Decap}}
\newcommand{\etm}{\monospace{EtM}}  % encrypt-then-mac
\newcommand{\mac}{\monospace{MAC}}
\newcommand{\sign}{\monospace{MAC}}
\newcommand{\verify}{\monospace{MAC.Verify}}
\newcommand{\pk}{\monospace{pk}}
\newcommand{\sk}{\monospace{sk}}
\newcommand{\pco}{\monospace{PCO}}
\newcommand{\cvo}{\monospace{CVO}}
\newcommand{\leftsample}{\stackrel{\$}{\leftarrow}}
\newcommand{\llbrack}{[\![}
\newcommand{\rrbrack}{]\!]}
\newcommand{\norm}[1]{\left\lvert #1 \right\rvert}
\newcommand{\fotplus}{\monospace{FOT+}}

@@

\section{The ``encrypt-then-MAC'' transformation}\label{sec:main-results}
Let $\pke(\keygen, \encrypt, \decrypt)$ be a public-key encryption scheme. Let $\mac$ be a deterministic message authentication code. Let $G: \mathcal{M}_\pke \rightarrow \mathcal{K}_\mac$ and $H: \{0,1\}^\ast \rightarrow \mathcal{K}_\kem$ be hash functions, where $\mathcal{K}_\kem$ denote the set of all possible session keys. The $\etm$ transformation outputs a key encapsulation mechanism $\kem_\etm(\keygen_\etm, \encap_\etm, \decap_\etm)$. The three routines are described in figure \ref{fig:etm-routines}.

\begin{figure}[H]
    \center
    \begin{minipage}{0.29\textwidth}
        \begin{algorithm}[H]
            \caption{$\keygen_\etm$}\label{alg:etm-keygen}
            \begin{algorithmic}[1]
                \State $(\pk, \sk_\pke) \leftsample \keygen(1^\lambda)$
                \State $z \leftsample \mathcal{M}_\pke$
                \State $\sk \leftarrow (\sk_\pke, z)$
                \State \Return $(\pk, \sk)$
            \end{algorithmic}
        \end{algorithm}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \begin{algorithm}[H]
            \caption{$\encap_\etm(\pk)$}\label{alg:etm-encap}
            \begin{algorithmic}[1]
                \State $m \leftsample \mathcal{M}_\pke$
                \State $k \leftarrow G(m)$
                \State $c \leftsample \encrypt(\pk, m)$
                \State $t \leftarrow \mac(k, c)$
                \State $K \leftarrow H(m, c)$
                \State \Return $((c, t), K)$
            \end{algorithmic}
        \end{algorithm}
    \end{minipage}
    \hfill
    \begin{minipage}{0.37\textwidth}
        \begin{algorithm}[H]
            \caption{$\decap_\etm(\sk, (c, t))$}\label{alg:etm-decap}
            \begin{algorithmic}[1]
                \State $(\sk_\pke, z) \leftarrow \sk$
                \State $\hat{m} \leftarrow \decrypt(\sk_\pke, c)$
                \State $\hat{k} \leftarrow G(\hat{m})$
                \If{$\mac(\hat{k}, c) \neq t$}
                    \State \Return $H(z, c)$
                \EndIf
                \State \Return $H(\hat{m}, c)$
            \end{algorithmic}
        \end{algorithm}
    \end{minipage}
    \caption{$\kem_\etm$ routines}\label{fig:etm-routines} 
\end{figure}

If the input $\pke$ is \monospace{OW-PCA} secure, then $\kem_\etm$ is \monospace{IND-CCA2} secure.

\begin{theorem}\label{thm:ow-pca-implies-kem-ind-cca2}
    For every \monospace{IND-CCA2} adversary $A$ against $\kem_\etm$ that makes at most $q_D$ decapsulation queries, there exists an \monospace{OW-PCA} adversary $B$ against the underlying $\pke$ such that

    \begin{equation*}
        \monospace{Adv}_\monospace{IND-CCA2}(A) \leq q_D \cdot \epsilon_\mac + 2 \cdot \monospace{Adv}_\monospace{OW-PCA}(B)
    \end{equation*}
\end{theorem}

\begin{proof}
    We will prove using a sequence of games. The complete sequence of games is shown in figure \ref{fig:sequence-of-games}

    \begin{figure}[H]
        \center
        \begin{minipage}{0.55\textwidth}
            \begin{algorithm}[H]
                \caption{Sequence of games $G_0 - G_3$}\label{alg:sequence-of-games}
                \begin{algorithmic}[1]
                    \State $(\pk, \sk) \leftsample \keygen(1^\lambda)$
                    \State $(m^\ast, z) \leftsample \mathcal{M}_\pke$
                    \State $k^\ast \leftarrow G(m^\ast)$
                        \Comment{Game 0-1}
                    \State $k^\ast \leftsample \mathcal{K}_\mac$
                        \Comment{Game 2-3}
                    \State $c^\ast \leftsample \encrypt(\pk, m^\ast)$
                    \State $t^\ast \leftarrow \mac(k^\ast, c^\ast)$
                    \State $K_0 \leftarrow H(m^\ast, c^\ast)$
                        \Comment{Game 0-2}
                    \State $K_0 \leftsample \mathcal{K}_\kem$
                        \Comment{Game 3}
                    \State $K_1 \leftsample \mathcal{K}_\kem$
                    \State $b \leftsample \{0,1\}$
                    \State $\hat{b} \leftarrow A^{\mathcal{O}^\decap}(
                        1^\lambda, \pk, (c^\ast, t^\ast), K_b)$
                        \Comment{Game 0}
                    \State $\hat{b} \leftarrow A^{\mathcal{O}^\decap_1}(
                        1^\lambda, \pk, (c^\ast, t^\ast), K_b)$
                        \Comment{Game 1-3}
                    \State \Return $\llbrack \hat{b} = b \rrbrack$
                \end{algorithmic}
            \end{algorithm}
        \end{minipage}
        \hfill
        \begin{minipage}{0.4\textwidth}
            \begin{algorithm}[H]
                \caption{$\mathcal{O}^\decap(c, t)$}\label{alg:etm-decap-oracle}
                \begin{algorithmic}[1]
                    \State $\hat{m} \leftarrow \decrypt(\sk_\pke, c)$
                    \State $\hat{k} \leftarrow G(\hat{m})$
                    \If{$\mac(\hat{k}, c) = t$}
                        \State \Return $H(\hat{m}, c)$
                    \EndIf
                    \State \Return $H(z, c)$
                \end{algorithmic}
            \end{algorithm}
            \begin{algorithm}[H]
                \caption{$\mathcal{O}^\decap_1(c, t)$}\label{alg:etm-decap-oracle-1}
                \begin{algorithmic}[1]
                    % TODO: this is ugly
                    \If{$\exists (\tilde{m}, \tilde{k}) \in \mathcal{L}^G :$ \\
                        $\;\;\;\;\decrypt(\sk_\pke, c) = \tilde{m}$ \\
                        $\;\;\;\;\;\land\; \mac(\tilde{k}, c) = t$}
                        \State \Return $H(\tilde{m}, c)$
                    \EndIf
                    \State \Return $H(z, c)$
                \end{algorithmic}
            \end{algorithm}
        \end{minipage}
        \caption{Sequence of games}\label{fig:sequence-of-games}
    \end{figure}

    % TODO: finish the proof
\end{proof}

@@

\subsection{Kyber using \fotplus}
\subsection{Performance comparisons}\label{sec:exp-results}
% TODO: Count how many Keccak permutations
% TODO: Count how many NTT operations
% 
Comparisons will do for Kyber and Kyber$^+$, define it.
